---
title: "Car crash Assignement"
author: "Miguel Angel Regueira"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
library(carcrashassignment)
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
knitr::opts_knit$set(root.dir = system.file("data", package = "carcrashassignment"))
```

Together with this package it has been distributed some sample data for years 2014 and 2015. First, let's generate expected file name and later let's load the data into a data frame.

```{r load_data}
make_filename(2014)
file <- file.path(system.file("data/", package = "carcrashassignment"), make_filename(2014))
data <- fars_read(file)
class(data)
str(data)
```

With function fars_read_years it can be obtained in a variable information of several years

```{r read_year}
data <- fars_read_years(years = c(2014, 2015))
class(data)
data
```

All this car accidents data can be summarize easily for a list of years to obtain the number of accidents per year per month.

```{r summary}
summary <- fars_summarize_years(years = c(2014, 2015))
knitr::kable(summary)
```

At last, car accidents occur during a year and in a state can be plotted, as in the following example for accidents in Florida in 2014.

```{r state}
fars_map_state(state.num = 12, year = 2014)
```


